Background Subtraction based on Deep Feature Transformation Learning Background Subtraction

### 2018-05-05 draft.tex
add fig1 to illustrate the idea of paper
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	modified:   draft.aux 	modified:   draft.log 	modified:   draft.pdf 	modified:   draft.tex

\section{Introduction}
% introduction 的第一段介绍这个问题为什么有做的意义
% 这个问题的意义
Background subtraction or foreground object detection is a fundamental problem of computer vision, 
which has been developed over the last few decades.
% 难点在哪
The main challenges of this problem comes from the diversely natural scenes,
such as the illumination variation \cite{2017_REVIEW_7914756}, wrapping tree \cite{2014_CVIU_SOBRAL20144} and running water \cite{Bouwmans2014}.
% 现状是什么
Previous work already achieve well performances in the scenes with low complexity.
% 现有的方法是怎么做的
In particular,
a large numbers of studies are focus designing artificial model according to the characteristic of a particular scenes.
%　效果如何
Example, the multiple background model are proposed for dynamic background,
and the texture are used to handle the shadow of objects.
%　为什么这个问题还有做下去的意义
However, in view of the continuous growth in videos obtained from diversely natural scenes,
more challenging scenes are proposed for background subtraction.
%　总结，这个问题很难，还能做
It remains a challenging problem to proposed a general solution for background subtraction in all exist and potential scenes.
%
% 
% 
% robust background 
% 
% via moving cameras
% in recent years, the matter of background subtraction for
% moving cameras has attracted sustained levels of interest from
% researchers
% 
% It is widely used as the pre-processing step of video processing, which can help us efficiently mark the region of interest, e.
% vehicles and humans, thus saving us huge amount of computing resources.
% Typically, Background subtraction is a binary classification task that assigns each pixel in a video sequence with a label, for either belonging to the background or foreground scene.

@@

sq1 = {p_1,p_2,...p_n} -> sq2 = {f_1,f_2,...f_n}                     (1)

@@

Elgammal et al.
introduced a probabilistic non-parametric method to model the background.
It is assumed that each background pixel is drawn from a PDF.
The PDF for each pixel is estimated with Kernel Density Estimation (KDE).

\subsection{region-based approach}
\label{sec_geo}
region-based approach assumpt that the neighbouring pixels have a similar variation as the pixel itself.

@@

In XXX, ss et al.
addressed scaling problems by reformulating principal component analysis for 2D images.
Meanwhile their method takes much lower memory consumption and computational cost than others.
Some online approaches have also been proposed recently, but they are still very computationally expensive.

\subsection{Algorithms based on Super-pixels}
\label{sec_sup}
A novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck.
They used a fixed background model, which was generated from a temporal median operation over N video frames.

@@

\section{The IFB Framework}
\label{sec3}
In this section, we introduce our DPVL model that consists of a pixels-based observation patches and a novel FCN networks for background subtraction.
We explain the details of the procedures of capturing the observation patches and the architecture of network in our DPVL model.
The complete system is illustrated in Figure XXX.
We use a set of input and ground true images to generalize the Pixels’ Variation Permutations, and reshape them into fixed-size image patches as and fed into a FCN.
After reassembling the patches into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.

@@

% Videos & GBSSP\cite{Lim2014_2014_ECCV} & calMoSeg\cite{2016_ECCV_Bideau2016}  & MLayer\cite{2017_ICCV_zhu2017multilayer}  & $\text{IFB}_{SU}$ & $\text{IFB}_{KA}$ & $\text{IFB}_{SI}$ & Videos & GBSSP\cite{Lim2014_2014_ECCV} & calMoSeg\cite{2016_ECCV_Bideau2016} & MLayer\cite{2017_ICCV_zhu2017multilayer}  &  $\text{IFB}_{SU}$ &  $\text{IFB}_{KA}$  &  $\text{IFB}_{SI}$  \\
\section{Conclusions}
In this paper,
we proposed the IFB framework for background subtraction for the case of a freely moving camera.
Unlike previous work in which attempts were made to improve the accuracy of the estimation of motion,
our IFB focuses on integrating rough foreground and background cues for foreground segmentation.
In particular, 
foreground cues are detected by a GMM model with the estimation of background motion,
while background cues are captured from spatio-temporal features filtered by homography transformation,
where the SURF\cite{2006_SURF}, KAZE\cite{2012_KAZE}, SIFT\cite{lowe2004distinctive} features are used as examples.
% the geometric constraints between the SIFT features.
Then, super-pixels under multiple levels are utilized to integrate these cues.
The efficiency of IFB results from the complementarity between foreground and background cues.
The accuracy of the proposed approach is improved though the utilization of super-pixels under multiple levels.
A comprehensive experiment to compare our results with the state-of-the-art shows the efficiency of our framework and points to its potential for use in practical applications.

>>>>

\section{Introduction}
% introduction 的第一段介绍这个问题为什么有做的意义
% 这个问题的意义
Background subtraction or foreground object detection is a fundamental problem of computer vision, 
which has been developed over the last few decades.
% 难点在哪
The main challenges of this problem comes from the diversely natural scenes,
such as the illumination variation \cite{2017_REVIEW_7914756}, wrapping tree \cite{2014_CVIU_SOBRAL20144} and running water \cite{Bouwmans2014}.
% 现状是什么
Previous work already achieve well performances in the scenes with low complexity.
% 现有的方法是怎么做的
In particular,
a large numbers of studies are focus designing artificial model according to the characteristic of a particular scenes.
%　效果如何
Example, the multiple background model are proposed for dynamic background,
and the texture are used to handle the shadow of objects.
%　为什么这个问题还有做下去的意义
However, in view of the continuous growth in videos obtained from diversely natural scenes,
more challenging scenes are proposed for background subtraction.
%　总结，这个问题很难，还能做
It remains a challenging problem to proposed a general solution for background subtraction in all exist and potential scenes.
%
% 
% 
% robust background 
% 
% via moving cameras
% in recent years, the matter of background subtraction for
% moving cameras has attracted sustained levels of interest from
% researchers
% 
% It is widely used as the pre-processing step of video processing, which can help us efficiently mark the region of interest, e.
% vehicles and humans, thus saving us huge amount of computing resources.
% Typically, Background subtraction is a binary classification task that assigns each pixel in a video sequence with a label, for either belonging to the background or foreground scene.
\begin{figure}[!t]	% FIGURE: figure/fig1 
\centering
\includegraphics[width=.5\textwidth]{figure/fig1}
\DeclareGraphicsExtensions.
    \caption{The illustration of Proposed approach}
\label{fig_FBMS_nobk}
\end{figure}

@@

% sq1 = {p_1,p_2,...p_n} -> sq2 = {f_1,f_2,...f_n}                     (1)

@@

Elgammal et al.
introduced a probabilistic non-parametric method to model the background.
It is assumed that each background pixel is drawn from a PDF.
The PDF for each pixel is estimated with Kernel Density Estimation (KDE).
\label{sec_geo}
region-based approach assumpt that the neighbouring pixels have a similar variation as the pixel itself.

@@

In XXX, ss et al.
addressed scaling problems by reformulating principal component analysis for 2D images.
Meanwhile their method takes much lower memory consumption and computational cost than others.
Some online approaches have also been proposed recently, but they are still very computationally expensive.
\label{sec_sup}
A novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck.
They used a fixed background model, which was generated from a temporal median operation over N video frames.

@@

\section{The  Framework}
\label{sec3}
In this section, we introduce our DPVL model that consists of a pixels-based observation patches and a novel FCN networks for background subtraction.
We explain the details of the procedures of capturing the observation patches and the architecture of network in our DPVL model.
The complete system is illustrated in Figure XXX.
We use a set of input and ground true images to generalize the Pixels’ Variation Permutations, and reshape them into fixed-size image patches as and fed into a FCN.
After reassembling the patches into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.

@@

% Videos & GBSSP\cite{Lim2014_2014_ECCV} & calMoSeg\cite{2016_ECCV_Bideau2016}  & MLayer\cite{2017_ICCV_zhu2017multilayer}  & $\text{IFB}_{SU}$ & $\text{IFB}_{KA}$ & $\text{IFB}_{SI}$ & Videos & GBSSP\cite{Lim2014_2014_ECCV} & calMoSeg\cite{2016_ECCV_Bideau2016} & MLayer\cite{2017_ICCV_zhu2017multilayer}  &  $\text{IFB}_{SU}$ &  $\text{IFB}_{KA}$  &  $\text{IFB}_{SI}$  \\
\section{Conclusions}
In this paper,
we proposed the framework for background subtraction for the case of pixels' historical observation.
Unlike previous work in which attempts were made to improve the accuracy of the estimation of motion,
our method focuses on transform the foreground cues for Background Subtruction.
In particular, 
pixels' historical observations are obtained from image blocks with the estimation of background motion,
% the geometric constraints between the SIFT features.
Then, super-pixels under multiple levels are utilized to integrate these cues.
The efficiency of historical observation from the complementarity between foreground and background cues.
A comprehensive experiment to compare our results with the state-of-the-art shows the efficiency of our framework and points to its potential for use in practical applications.
